Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-09-04 paper/tex/methods.tex
addressing comments from @sschmidt23

We test three publicly available and commonly used template-based codes that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a \chisq\ merit function using the observed and model fluxes:
\begin{equation} \label{eq_temp_chi}
\chi^2(z,T,A) = \sum_i^{N_{\rm filt}}\left(\frac{F^i_{\rm{obs}} - A \, F^i_{\rm{pred}}(T,z)}{\sigma^i_{\rm{obs}}}\right)^2
\end{equation}
\noindent where $A$ is a normalization factor, $F^i_{\rm{pred}}(T,z)$ is the flux predicted for a template $T$ at redshift $z$, $F^i_{\rm{obs}}$ is the observed flux in a given band $i$, $\sigma^i_{\rm{obs}}$ is the observed flux error, and $N_{\rm filt}$ is the total number of filters, in our case the six $ugrizy$ LSST filters.
In words, the likelihood is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which is the \lsst\ $ugrizy$ filters in this case.
Specific implementation details of each code, e.~g.~prior form and implementation, are described below.

@@

Here we use \lephare-v 2.2 with the DC1 template set of Section~\ref{sec:buzztemplates}.

Bayesian Photometric Redshift \citep[\bpz\footnote{\url{http://www.stsci.edu/~dcoe/BPZ/}},][]{Benitez:00} determines the likelihood $p(C \vert z, T)$ of a galaxy's observed colours $C$ for a set of SED templates $T$ at redshifts $z$.
The \bpz\ likelihood is related to the \chisq\ likelihood by $p(C \vert z, T) \propto \exp[- \chi^{2} / 2]$.
Given a Bayesian prior $p(z, T \vert m_{0})$ over apparent magnitude $m_0$ and type $T$, and assuming that the SED templates are spanning and exclusive, \bpz\ constructs the redshift posterior $p(z \vert C, m_0)$ by marginalizing over all SED templates with the form $p(z|C,m_0)\,\propto\, \sum_{T}p(C|z,T)\,p(z,T|m_0)$ \citep[Eq.~3 from][]{Benitez:00}, corresponding to setting the parameter \texttt{PROBS\_LITE=TRUE} in the \bpz\ parameter file.
The \bpz\ prior is the product of an SED template proportion that varies with apparent magnitude $p(T \vert m_{0})$ and a prior $p(z \vert T, m_{0})$ over the expected redshift as a function of apparent magnitude and SED template.

Here we test \bpz-v 1.99.3 with the DC1 template set of Section~\ref{sec:buzztemplates}.
To keep the number of free parameters manageable, the DC1 template set is pre-sorted by the rest-frame $u-g$ colour and split into three broad classes of SED template, equivalent to the E, Sp and Im/SB types.
The Bayesian prior term $p(T \vert m_{0})$ was derived directly from the DC1 training set, and the other term $p(z \vert T, m_{0})$ was chosen to be the best fit for the eleven free parameters of the functional form of \citet{Benitez:00}.
We use template interpolation, creating two linearly interpolated templates between each basis SED (sorted by rest-frame $u-g$ colour) by setting the parameter \texttt{INTERP=2}.
%For photo-$z$ point estimates we use the \texttt{Z\_B} output parameter.
Prior to running the code, the non-detection placeholder magnitude was replaced with an estimate of the one-$\sigma$ detection limit for the undetected band as a proxy for a value close to the estimated sky noise threshold.

Easy and Accurate Photometric Redshifts from Yale \citep[\eazy\footnote{\url{https://github.com/gbrammer/eazy-photoz}},][]{Brammer:08} extends the basic \chisq\ fit procedure that defines template-fitting approaches.
The algorithm models the observed photometry with a linear combination of template SEDs at each redshift.
The best-fit SED is found by simultaneously fitting one, two, or all of the templates via \chisq\ minimization, which is distinct from marginalizing across all templates.
The minimized \chisq\ likelihood at each redshift is then combined with an apparent magnitude prior to obtain the redshift posterior PDF.
We note that the utilization of the best-fit SED rather than a proper marginalization does not lead to the correct posterior distribution, an implementation issue that has now been identified and will be addressed by the developers in the future.
\eazy\ can account for uncertainty in the template set by adding in quadrature to the flux errors an empirically derived template error as a function of redshift.

The SED-independent apparent magnitude prior was derived empirically from the DC1 training set.
The \eazy\ architecture cannot accept a template set other than the same five basis templates employed by \texttt{k-correct} when constructing the DC1 catalogue.
However, \eazy\ does feature a flexible \texttt{all-templates} mode, which fits the photometric data with a linear combination of the five basis templates.
We set the template error to zero since the same templates were in fact used to produce the DC1 photometry.

@@

\annz \footnote{\url{https://github.com/IftachSadeh/ANNZ}} \citep{Sadeh:16} employs several machine learning algorithms, including artificial neural networks (ANN), boosted decision tree, and k-nearest neighbour (KNN) regression.
In addition to accounting for errors on the input photometry, \annz\ uses the KNN-uncertainty estimate of \citet{Oyaizu:08} to quantify uncertainty in the choice of method over multiple runs.
Using the Toolkit for Multivariate Data Analysis with ROOT\footnote{\url{http://tmva.sourceforge.net/}}, \annz\ can return the results of running a single machine learning algorithm, a ``best'' choice of the results from simultaneously running multiple algorithms (based on evaluation the cumulative distribution functions of validation set objects), or a combination of the results of multiple algorithms weighted by their method uncertainties averaged over multiple runs.
%\textsc{ANNz2} is capable of producing both photo-$z$ point estimates and redshift posterior probability distributions $p(z)$.
% It can also perform classifications, and supports reweighting between samples.
% \annz\ propagates the intrinsic uncertainty on the input parameters and the uncertainty in the machine learning method to the expected photo-$z$ solution, averaged over multiple runs weighted based on the performance of each run.

In this study, we used \annz-v.2.0.4 to output only the result of the ANN algorithm.
\Pzpdf s were produced by running an ensemble of 5 ANNs with a $6:12:12:1$ architecture corresponding to the 6 $ugrizy$ inputs, 2 hidden layers with 12 nodes each, and 1 output of redshift.
Each of the five ANNs was trained with different random seeds for the initialization of input parameters.
Additionally, all ANNs were trained on only a $i \leq 25.3$ subsample of the DC1 training set, and half of the training set was reserved for validation to prevent overfitting.
Undetected galaxies were excluded from the training set, and per-band non-detections in the test set were replaced with the mean magnitude in that band within the entire test set.

@@

The nearest-neighbours colour-matching photometric redshift estimator \citep[\cmnn,][]{Graham:17} uses a training set of galaxies with known redshifts that has equivalent or better photometry than the test set in terms of quality and filter coverage.
For each galaxy in the test set, \cmnn\ identifies a colour-matched subset of training galaxies using a threshold in the Mahalanobis distance $D_M = \sum_{j}^{N_{\rm colours}} (c^{\rm train}_{j} - c^{\rm test}_{j})^{2} / \delta c_{\rm test}^2$ in the space of available colours $c$, with colour measurement errors $\delta c_{\rm test}$ and $N_{\rm colours} = 5$ colors $j$ defined by the $ugrizy$ filters, which defines the set of colour-matched neighbours based on a value of the percent point function (PPF).
As an example, for $N_{\rm{filt}}=5$ with PPF$=0.95$, $95\%$ of all training galaxies consistent with the test galaxy will have $D_M < 11.07$.
Undetected bands are dropped, thereby reducing the effective $N_{\rm{filt}}$ for that galaxy.
The \pzpdf\ of a given test set galaxy is the normalized distribution of redshifts of its colour-matched subset of training set galaxies.

@@

We make an additional adaptation to enable the \cmnn\ algorithm to yield accurate \pzpdf s for all galaxies, as the original \citet{Graham:17} algorithm is optimized for \pz\ point estimates and is susceptible to less accurate \pzpdf s for bright galaxies or those with few matches in colour-space.
We use PPF$=0.95$ rather than PPF$=0.68$ to generate the subset of colour-matched training galaxies, whose redshifts are weighted by their inverse Mahalanobis distances of the when composing the \pzpdf\ rather than weighting all colour-matched training galaxies equally.
Additionally, when the number of colour-matched training set galaxies is less than 20, the nearest 20 neighbours in color-space are used instead, and the output \pzpdf\ is convolved with a Gaussian kernel of variance $\sigma_{\rm train}^{2}({\rm PPF}_{20}/0.95)^2 -1$ to account foe the corresponding growth of the effective PPF to include 20 neighbors.

@@

\gpz \footnote{\url{https://github.com/OxfordML/GPz}} \citep{Almosallam:16a,Almosallam:15b} is a sparse Gaussian process based code, a scalable approximation of full Gaussian Processes \citep{Rasmussen:06}, that produces input-dependent variance estimates corresponding to heteroscedastic noise.
The model assumes a Gaussian posterior probability $p(z \vert \x) = \mathcal{N}\left(z \vert \mu(\x), \sigma(\x)^{2}\right)$ of the output redshift $z$ given the input photometry $\x$.
The mean $\mu(\x)$ and the variance $\sigma(\x)^{2}$ are modeled as functions $f(\x) = \sum_{i=1}^{m}w_{i}\phi_{i}(\x)$ linear combinations of $m$ basis functions $\left\{\phi_{i}(\x)\right\}_{i=1}^{m}$ with associated weights $\left\{w_{i}\right\}_{i=1}^{m}$.
% Basis function models, for specific classes of basis functions such as the sigmoid or the squared exponential, have the advantage of being universal approximators, i.e. there exist a function of that form that can approximate any function, with mild assumptions, to any desired degree of accuracy.
The details on how to learn the parameters of the model and the hyper-parameters of the basis functions are described in \citet{Almosallam:15b}.
\gpz's variance estimate is composed of a model uncertainty term corresponding to sparsity of the training set photometry and a noise uncertainty term encompassing noisy photometric observations, enabling quantification of any need for more representative or more precise training samples.
\gpz\ may also weight training set samples by importance according to $|z_{\rm{spec}} - z_{\rm{phot}}| / (1+z_{\rm{spec}})$ to minimize the normalized \pz\ point estimate error, however, this function may be adapted to \pzpdf s, pressuring the model to dedicate more resources to test set galaxies that are not well-represented in the training set.

To smooth the long tail in the distribution of magnitude errors, we use the log of the magnitude errors, improving numerical stability and eliminating the need for constraints on the optimization process.
% We use principaphoto-\mathinhead{$z$}{z} interim posteriorsl component analysis (PCA) to decorrelate the data
% WHAT IS BEING DECORRELATED HERE?
Unobserved magnitudes $x_{\rm u} = \mu_{\rm u} + \Sigma_{\rm uo}\Sigma_{\rm oo}^{-1}(x_{\rm o} - \mu_{\rm o})$ were imputed from observed magnitudes $x_{\rm o}$ and the training set mean $\mu$ and covariance $\Sigma$ using a linear model.
This is the optimal expected value of the unobserved variables given the observed ones under the assumption that the distribution is jointly Gaussian; note that this reduces to a simple average if the covariates are independent with $\Sigma_{\rm uo} = 0$.
We reserved for validation 20\% of the training set and used the Variable Covariance option in \gpz\ with 200 basis functions (see \citet{Almosallam:15b} for details), neglecting to apply cost-sensitive learning options.

@@

\skynet \footnote{\url{http://ccpforge.cse.rl.ac.uk/gf/project/skynet/}} \citep{Graff:14} employs a neural network based on a second order conjugate gradient optimization scheme \citep[see][for further details]{Graff:14}. %It has been used efficiently for redshift PDF estimates \citep{Sanchez:14,Bonnett:15,Bonnett:16}.
The neural network is configured as a standard multilayer perceptron with three hidden layers and one input layer with 12 nodes corresponding to the 6 photometric magnitudes and their measurement errors.
We use \skynet\ as a regressor for \pz\ point estimation and as a classifier for \pzpdf\ estimation.

The regressor used a standard \chisq\ error function with a single linear node as the output layer and 10 nodes with a $\tanh$ activation function for each hidden layer.
The classifier used a cross-entropy error function with a 20:40:40 node (all rectified linear units) architecture for each hidden layer and an output layer of 200 nodes corresponding to 200 bins for the PDF, with a softmax activation function to enforce the normalization condition that the probabilities sum to unity.
While previous implementations of the code \citep[see Appendix C.3 of~][]{Sanchez:14,Bonnett:15} implement a sliding bin smoothing, no such procedure was used in this study.

@@

\subsection{trainZ: a pathological \pz\ estimator}
\label{sec:trainz}

We also consider a pathological \pzpdf\ estimation method, dubbed \trainz, which assigns each test set galaxy a \pzpdf\ equal to the normalized redshift distribution $N(z)$ of the training set, according to
\begin{equation}
	p(z \vert \{z_{j}\}) \equiv \frac{1}{N_{ \mathrm train}}\sum_{\mathrm i=1}^{N_{\mathrm train}} \begin{cases} 1 & \text{if\ } z_{k}\leq z_{i} < z_{k+1}\\ 0 & \text{otherwise} \end{cases}.
\end{equation}
Unlike the other methods, the \trainz\ estimator is \textit{independent of the photometric data}, effectively performing a KNN procedure with $k=N_{\rm train}$.

>>>>

We test three publicly available and commonly used template-based codes that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a \chisq\ merit function using the observed and model fluxes:
\begin{equation} \label{eq_temp_chi}
\chi^{2}(z,T,A) = \sum_{i}^{N_{\mathrm{filt}}}\left(\frac{F^{i}_{\mathrm{obs}} - A \, F^{i}_{\mathrm{pred}}(T,z)}{\sigma^{i}_{\mathrm{obs}}}\right)^2
\end{equation}
\noindent where $A$ is a normalization factor, $F^i_{\mathrm{pred}}(T,z)$ is the flux predicted for a template $T$ at redshift $z$, $F^i_{\mathrm{obs}}$ is the observed flux in a given band $i$, $\sigma^i_{\mathrm{obs}}$ is the observed flux error, and $N_{\mathrm filt}$ is the total number of filters, in our case the six $ugrizy$ LSST filters.
In words, the likelihood is a sum of observed flux error $\sigma_{b}^{\mathrm{obs}}$-weighted squared differences between the observed flux $F^{\mathrm{obs}}_{b}$ and the normalized predicted flux $F^{\mathrm{mod}}_{b}(T, z)$ in $N_{\mathrm{filt}}$ photometric filters $b$, which is the \lsst\ $ugrizy$ filters in this case.
Specific implementation details of each code, e.~g.~prior form and implementation, are described below.

Bayesian Photometric Redshift \citep[\bpz\footnote{\url{http://www.stsci.edu/~dcoe/BPZ/}},][]{Benitez:00} determines the likelihood $p(C \vert z, T)$ of a galaxy's observed colours $C$ for a set of SED templates $T$ at redshifts $z$.
The \bpz\ likelihood is related to the \chisq\ likelihood by $p(C \vert z, T) \propto \exp[- \chi^{2} / 2]$.
Given a Bayesian prior $p(z, T \vert m_{0})$ over apparent magnitude $m_0$ and type $T$, and assuming that the SED templates are spanning and exclusive, \bpz\ constructs the redshift posterior $p(z \vert C, m_0)$ by marginalizing over all SED templates with the form $p(z|C,m_0)\,\propto\, \sum_{T}p(C|z,T)\,p(z,T|m_0)$ \citep[Eq.~3 from][]{Benitez:00}, corresponding to setting the parameter \texttt{PROBS\_LITE=TRUE} in the \bpz\ parameter file.
The \bpz\ prior is the product of an SED template proportion that varies with apparent magnitude $p(T \vert m_{0})$ and a prior $p(z \vert T, m_{0})$ over the expected redshift as a function of apparent magnitude and SED template.
We anticipate \bpz\ to outperform other template-based approaches due to the prior that both comprehensively accounts for SED type and is calibrated to the training set.

Here we test \bpz-v 1.99.3 \citep{Benitez:00} with the DC1 template set of Section~\ref{sec:buzztemplates}.
To keep the number of free parameters manageable, the DC1 template set is pre-sorted by the rest-frame $u-g$ colour and split into three broad classes of SED template, equivalent to the E, Sp and Im/SB types.
The Bayesian prior term $p(T \vert m_{0})$ was derived directly from the DC1 training set, and the other term $p(z \vert T, m_{0})$ was chosen to be the best fit for the eleven free parameters from the functional form of \citet{Benitez:00}.
We use template interpolation, creating two linearly interpolated templates between each basis SED (sorted by rest-frame $u-g$ colour) by setting the parameter \texttt{INTERP=2}.
%For photo-$z$ point estimates we use the \texttt{Z\_B} output parameter.
Prior to running the code, the non-detection placeholder magnitude was replaced with an estimate of the one-$\sigma$ detection limit for the undetected band as a proxy for a value close to the estimated sky noise threshold.

Easy and Accurate Photometric Redshifts from Yale \citep[\eazy\footnote{\url{https://github.com/gbrammer/eazy-photoz}},][]{Brammer:08} extends the basic \chisq\ fit procedure that defines template-fitting approaches.
The algorithm models the observed photometry with a linear combination of template SEDs at each redshift.
The best-fit SED at each redshift is found by simultaneously fitting one, two, or all of the templates via \chisq\ minimization, which is distinct from marginalizing across all templates.
The minimized \chisq\ likelihood at each redshift is then combined with an apparent magnitude prior to obtain the redshift posterior PDF.
We note that the utilization of the best-fit SED conditioned on redshift rather than a proper marginalization does not lead to the correct posterior distribution, an implementation issue that has now been identified and will be addressed by the developers in the future.

In contrast with \bpz, \eazy's apparent magnitude prior is independent of SED, though it was derived empirically from the DC1 training set.
The \eazy\ architecture cannot accept a template set other than the same five basis templates employed by \texttt{k-correct} when constructing the DC1 catalogue, but, for consistency with the experimental scope of perfect prior information, \eazy's flexible \texttt{all-templates} mode was used to fit the photometric data with a linear combination of the five basis templates.
Though \eazy\ can account for uncertainty in the template set by adding in quadrature to the flux errors an empirically derived template error as a function of redshift, we set the template error to zero since the same templates were in fact used to produce the DC1 photometry.

@@

Here we use \lephare-v 2.2 with the DC1 template set of Section~\ref{sec:buzztemplates}.
Unlike both \bpz\ and \eazy, \lephare\ uses generic, SED-independent priors that are not tuned to the DC1 data set.

@@

\annz \footnote{\url{https://github.com/IftachSadeh/ANNZ}} \citep{Sadeh:16} supports several machine learning algorithms, including artificial neural networks (ANN), boosted decision tree, and k-nearest neighbour (KNN) regression.
In addition to accounting for errors on the input photometry, \annz\ uses the KNN-uncertainty estimate of \citet{Oyaizu:08} to quantify uncertainty in the choice of method over multiple runs.
Using the Toolkit for Multivariate Data Analysis with ROOT\footnote{\url{http://tmva.sourceforge.net/}}, \annz\ can return the results of running a single machine learning algorithm, a ``best'' choice of the results from simultaneously running multiple algorithms (based on evaluation the cumulative distribution functions of validation set objects), or a combination of the results of multiple algorithms weighted by their method uncertainties averaged over multiple runs.
%\textsc{ANNz2} is capable of producing both photo-$z$ point estimates and redshift posterior probability distributions $p(z)$.
% It can also perform classifications, and supports reweighting between samples.
% \annz\ propagates the intrinsic uncertainty on the input parameters and the uncertainty in the machine learning method to the expected photo-$z$ solution, averaged over multiple runs weighted based on the performance of each run.

In this study, we used \annz-v.2.0.4 to output only the result of the ANN algorithm.
\Pzpdf s were produced by running an ensemble of 5 ANNs with a $6:12:12:1$ architecture corresponding to the 6 $ugrizy$ inputs, 2 hidden layers with 12 nodes each, and 1 output of redshift.
Each of the five ANNs was trained with different random seeds for the initialization of input parameters, reserving half of the training set for validation to prevent overfitting.
Undetected galaxies were excluded from the training set, and per-band non-detections in the test set were replaced with the mean magnitude in that band within the entire test set.

@@

The colour-matched nearest-neighbours photometric redshift estimator \citep[\cmnn,][]{Graham:17} uses a training set of galaxies with known redshifts that has equivalent or better photometry than the test set in terms of quality and filter coverage.
For each galaxy in the test set, \cmnn\ identifies a colour-matched subset of training galaxies using a threshold in the Mahalanobis distance $D_M = \sum_{j}^{N_{\mathrm{colours}}} (c^{\mathrm{train}}_{j} - c^{\mathrm{test}}_{j})^{2} / \delta c_{\mathrm{test}}^2$ in the space of available colours $c$, with colour measurement errors $\delta c_{\mathrm{test}}$ and $N_{\mathrm{colours}} = 5$ colors $j$ defined by the $ugrizy$ filters, which defines the set of colour-matched neighbours based on a value of the percent point function (PPF).
As an example, for $N_{\mathrm{filt}}=5$ with PPF$=0.95$, $95\%$ of all training galaxies consistent with the test galaxy will have $D_M < 11.07$.
Undetected bands are dropped, thereby reducing the effective $N_{\mathrm{filt}}$ for that galaxy.
The \pzpdf\ of a given test set galaxy is the normalized distribution of redshifts of its colour-matched subset of training set galaxies.

@@

We make an additional adaptation to enable the \cmnn\ algorithm to yield accurate \pzpdf s for all galaxies, as the original \citet{Graham:17} algorithm is optimized for \pz\ point estimates and is susceptible to less accurate \pzpdf s for bright galaxies or those with few matches in colour-space.
We use PPF$=0.95$ rather than PPF$=0.68$ to generate the subset of colour-matched training galaxies, whose redshifts are weighted by their inverse Mahalanobis distances of the when composing the \pzpdf\ rather than weighting all colour-matched training galaxies equally.
Additionally, when the number of colour-matched training set galaxies is less than 20, the nearest 20 neighbours in color-space are used instead, and the output \pzpdf\ is convolved with a Gaussian kernel of variance $\sigma_{\mathrm{ train}}^{2}(\mathrm{PPF}_{20}/0.95)^2 -1$ to account for the corresponding growth of the effective PPF to include 20 neighbors.

@@

\gpz \footnote{\url{https://github.com/OxfordML/GPz}} \citep{Almosallam:16a,Almosallam:15b} is a sparse Gaussian process based code, a scalable approximation of full Gaussian Processes \citep{Rasmussen:06}, that produces input-dependent variance estimates corresponding to heteroscedastic noise.
The model assumes a Gaussian posterior probability $p(z \vert \x) = \mathcal{N}\left(z \vert \mu(\x), \sigma(\x)^{2}\right)$ of the output redshift $z$ given the input photometry $\x$.
The mean $\mu(\x)$ and the variance $\sigma(\x)^{2}$ are modeled as functions $f(\x) = \sum_{i=1}^{m}w_{i}\phi_{i}(\x)$ linear combinations of $m$ basis functions $\left\{\phi_{i}(\x)\right\}_{i=1}^{m}$ with associated weights $\left\{w_{i}\right\}_{i=1}^{m}$.
% Basis function models, for specific classes of basis functions such as the sigmoid or the squared exponential, have the advantage of being universal approximators, i.e. there exist a function of that form that can approximate any function, with mild assumptions, to any desired degree of accuracy.
The details on how to learn the parameters of the model and the hyper-parameters of the basis functions are described in \citet{Almosallam:15b}.
\gpz's variance estimate is composed of a model uncertainty term corresponding to sparsity of the training set photometry and a noise uncertainty term encompassing noisy photometric observations, enabling quantification of any need for more representative or more precise training samples.
\gpz\ may also weight training set samples by importance according to $|z_{\mathrm{spec}} - z_{\mathrm{phot}}| / (1+z_{\mathrm{spec}})$ to minimize the normalized \pz\ point estimate error, however, this function may be adapted to \pzpdf s, pressuring the model to dedicate more resources to test set galaxies that are not well-represented in the training set.

To smooth the long tail in the distribution of magnitude errors, we use the log of the magnitude errors, improving numerical stability and eliminating the need for constraints on the optimization process.
% We use principaphoto-\mathinhead{$z$}{z} interim posteriorsl component analysis (PCA) to decorrelate the data
% WHAT IS BEING DECORRELATED HERE?
Unobserved magnitudes $x_{\mathrm{u}} = \mu_{\mathrm{u}} + \Sigma_{\mathrm{uo}}\Sigma_{\mathrm{oo}}^{-1}(x_{\mathrm{o}} - \mu_{\mathrm{o}})$ were imputed from observed magnitudes $x_{\mathrm{o}}$ and the training set mean $\mu$ and covariance $\Sigma$ using a linear model.
This is the optimal expected value of the unobserved variables given the observed ones under the assumption that the distribution is jointly Gaussian; note that this reduces to a simple average if the covariates are independent with $\Sigma_{\mathrm{uo}} = 0$.
We reserved for validation 20\% of the training set and used the Variable Covariance option in \gpz\ with 200 basis functions (see \citet{Almosallam:15b} for details), neglecting to apply cost-sensitive learning options.

@@

\skynet \footnote{\url{http://ccpforge.cse.rl.ac.uk/gf/project/skynet/}} \citep{Graff:14} employs a neural network based on a second order conjugate gradient optimization scheme \citep[see][for further details]{Graff:14}. %It has been used efficiently for redshift PDF estimates \citep{Sanchez:14,Bonnett:15,Bonnett:16}.
The neural network is configured as a standard multilayer perceptron with three hidden layers and one input layer with 12 nodes corresponding to the 6 photometric magnitudes and their measurement errors.
% We use \skynet\ as a regressor for \pz\ point estimation and as a classifier for \pzpdf\ estimation.

% The regressor used a standard \chisq\ error function with a single linear node as the output layer and 10 nodes with a $\tanh$ activation function for each hidden layer.
\skynet's classifier mode uses a cross-entropy error function with a 20:40:40 node (all rectified linear units) architecture for each hidden layer and an output layer of 200 nodes corresponding to 200 bins for the PDF, with a softmax activation function to enforce the normalization condition that the probabilities sum to unity.
While previous implementations of the code \citep[see Appendix C.3 of~][]{Sanchez:14,Bonnett:15} implement a sliding bin smoothing, no such procedure was used in this study.

@@

\subsection{trainZ: a pathological \pzpdf\ estimator}
\label{sec:trainz}

We also consider a pathological \pzpdf\ estimation method, dubbed \trainz, which assigns each test set galaxy a \pzpdf\ equal to the normalized redshift distribution $N(z)$ of the training set, according to
\begin{equation}
	p(z \vert \{z_{j}\}) \equiv \frac{1}{N_{ \mathrm train}}\sum_{\mathrm i=1}^{N_{\mathrm train}} \begin{cases} 1 & \text{if\ } z_{k}\leq z_{i} < z_{k+1}\\ 0 & \text{otherwise} \end{cases}.
\end{equation}
Unlike the other methods, the \trainz\ estimator is \textit{independent of the photometric data}, effectively performing a KNN procedure with $k=N_{\mathrm{train}}$.

### 2019-09-04 paper/tex/results.tex
addressing comments from @sschmidt23

The most striking differences between codes are due to small-scale features induced by the interaction between the shared piecewise constant parameterization of $200$ bins $0 < z < 2$ of Section~\ref{sec:metrics} and the smoothing conditions or lack thereof in each algorithm.
The $\rm{d}z = 0.01$ redshift resolution is sufficient to capture the broad peaks of faint galaxies' \pzpdf s with large photometric errors but is too broad to resolve the narrow peaks for bright galaxies' \pzpdf s with small photometric errors.
This observation is consistent with the findings of \citet[]{Malz:qp} that the piecewise constant parameterization underperforms in the presence of small-scale structures.

@@

The values of the CDE loss statistic of individual \pzpdf\ accuracy are provided in Table~\ref{tab:cdeloss}.
It is worth noting that strong performance on the CDE loss should imply strong performance on the other metrics, though the inverse is not necessarily true.
Thus the CDE loss is the most effective metric for generic science cases.

@@

This metric is the only one that can appropriately penalize \trainz\ and indicates strong performance for \cmnn\ and \flexzboost, the latter of which is optimized for this metric.

>>>>

The most striking differences between codes are the small-scale features induced by the interaction between the shared piecewise constant parameterization of $200$ bins $0 < z < 2$ of Section~\ref{sec:metrics} and the smoothing conditions or lack thereof in each algorithm.
The $\mathrm{d}z = 0.01$ redshift resolution is sufficient to capture the broad peaks of faint galaxies' \pzpdf s with large photometric errors but is too broad to resolve the narrow peaks for bright galaxies' \pzpdf s with small photometric errors.
This observation is consistent with the findings of \citet[]{Malz:2018} that the piecewise constant parameterization underperforms in the presence of small-scale structures.

@@

The values of the CDE loss statistic of individual \pzpdf\ accuracy are provided in Table~\ref{tab:cdeloss}.
It is worth noting that strong performance on the CDE loss, corresponding to lower values of the metric, should imply strong performance on the other metrics, though the inverse is not necessarily true.
Thus the CDE loss is the most effective metric for generic science cases.

@@

Of the metrics we were able to consider in this experiment, \textbf{the CDE Loss is the only metric that can appropriately penalize the pathological\trainz}.
Additionally, it favors \cmnn\ and \flexzboost, the latter of which is optimized for this metric.
